---
title: "Toronto Citizens' Opinion on A Future Casinos"
subtitle: "For vs. Against And General Preferences"
author: 
  - Ying Wen Bu
thanks: "Code and data are available at: https://github.com/annie142857/starter_folder/tree/main"
date: 19 September 2024
date-format: long
abstract: "This study takes results from a Toronto City Manager's survey on people's opinion on the construction of a casino. Over half of the respondents were strongly against this casino. In the consideration of various entertainments, participants generally showed a preference for healthy recreations and refusal of potentially harmful pastimes. Although the survey was conducted to incorporate people's viewpoint into the casino's construction, the results can still be used in other research to investigate people's opinions on casinos and related entertainments."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)

approval <- read_csv(here::here("C:/Users/86189/Desktop/STA304A1/outputs/data/clean_data(approval).csv"), show_col_types = FALSE)

standalone <- read_csv(here::here("C:/Users/86189/Desktop/STA304A1/outputs/data/clean_data(standalone).csv"), show_col_types = FALSE)

summarytbl <- read_csv(here::here("C:/Users/86189/Desktop/STA304A1/outputs/data/clean_data(summarytbl).csv"), show_col_types = FALSE)

```


# Introduction

The casino survey data is taken from @opendatatoronto. Then, @citeR, @tidyverse, @dplyr, @ggplot2, and @rotate are used to clean, modify, and graph the data for analysis.

The remainder of this paper is structured as follows. First, the explanation of the data followed by the result section, which contains three graphs and their analysis.


# Data {#sec-datasection}

In 2013, the City Manager of Toronto collaborated with the company DPRA to collect public opinion on the construction of a casino in Toronto. This study examines responses to several questions in this survey. The first four variables, which were plotted in @fig-approval and @fig-standalone, are responses to multiple choice problems that ask participants to evaluate the city's decisions. The last ten variables were types of entertainment for participants to decide on their appropriateness to be included in an integrated entertainment complex. They are plotted in @fig-summarytbl.
There is another casino survey on Open Data Toronto, and it was done in 2015, on expanding casino at Woodbine Racetrack. However, in terms of that survey, Open Data Toronto only provides the questions asked, but not the responses, so that survey cannot be investigated. During the cleaning, NA values were dropped, and the values of the last ten variables were counted using summarize and then entered into a new table, whereas the first four variables were counted during graphing. The last ten variables cannot be counted during the graphing because they are in individual columns and recorded in terms of TRUE or FALSE.

# Results

```{r}
#| echo: false
#| eval: true
#| warning: false
#| label: fig-approval
#| fig-cap: "Attitude towards A New Casino"
#| fig-subcap: ["How you feel about a new casino?","Does a casino fit your image of the city?"]
#| layout-ncol: 2

approval |>
  ggplot(aes(x = feeling, fill = Gender)) +
  geom_bar() +
  theme_classic() +
  labs(x = "Feeling about having a new casino", y = "Number of respondents")

approval |>
  ggplot(aes(x = image, fill = Gender)) +
  geom_bar() +
  theme_classic() +
  labs(x = "Does it fit the image of the city", y = "Number of respondents")
```

Participants were asked on their feelings about having a new casino in Toronto, as shown in @fig-approval-1, where 1 means strongly opposed and 5 means strongly in favor. Almost 10000 participants strongly opposed the new casino, which is over half of the respondents. This tendency is slightly higher in women. Due to the low number of transgender participants, no observation can be drawn on their tendencies on this problem. Most of the participants have a strong opinion on this problem, and they either strongly opposed or are strongly in favor of a casino.

Participants were then asked on whether a new casino fit their image of Toronto. This question is similar to the previous question, although it only have four options instead of five. The responses were very similar to those of the previous question, except that the "not at all" option exceeded 10000 respondents, presumably because it contained participants from the two "opposed" options from the previous question.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| label: fig-standalone
#| fig-cap: "How suitable is each type of building?"
#| fig-subcap: ["How suitable is a standalone casino?","How suitable is an integrated entertainment complex?"]
#| layout-ncol: 2

standalone |>
  ggplot(aes(x = standalone, fill = Gender)) +
  geom_bar() +
  theme_classic() +
  labs(x = "Suitability", y = "Number of respondents")

standalone |>
  ggplot(aes(x = integrated, fill = Gender)) +
  geom_bar() +
  theme_classic() +
  labs(x = "Suitability", y = "Number of respondents")
```

Participants were asked to rate the suitability of a standalone casino (fig-standalone-1), and the suitability of an integrated entertainment complex casino (fig-standalone-2). In the graphs, 1 means strongly unsuitable, and 5 means strongly suitable. For both types of buildings, the majority of participants selected "strongly unsuitable". This tendency is slightly higher in women and in people who preferred to not disclose their gender. Nothing can be drawn on transgender people because their number is too low. Around 10000 participants found a standalone casino strongly unsuitable, while this number is lower than 9000 for an integrated entertainment complex with casino, showing a slightly higher tolerance of an integrated entertainment complex.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| label: fig-summarytbl
#| fig-cap: "What should a future Integrated Entertainment Complex include?"

summarytbl |>
  mutate(
    entertainment_as_factor = factor(entertainment),
    entertainment_as_factor = fct_relevel(
      entertainment,
      "no casino",
      "casino only",
      "convention centre",
      "hotel",
      "culture & arts",
      "retail",
      "nightclub",
      "theatre",
      "restaurant",
      "other"
    )
  ) |>
  ggplot(aes(x = entertainment_as_factor, y = participants)) +
  geom_bar(stat = "identity") +
  theme_classic() +
  labs(x = "Entertainment", y = "Number of Votes") +
# Code from @rotate, or How to Rotate Axis Labels in ggplot2? is used in the next line
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
```

Participants were asked on what should be included in a future integrated entertainment complex, as shown in @fig-summarytbl, which was plotted with the help of @rotate. Slightly over 10000 participants voted for no casino, which was very consistent with the number of votes that were against casino in the previous few questions. Over 1000 participants voted for casino only. Further research could take a look at the explanations for this in the survey. For the other entertainments, the highest votes are on culture & arts, theatre, and restaurant, while the lowest votes are on nightclub and other. 


# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}


# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check




\newpage


# References