---
title: "Fluctuation of Marriage License Data by Time"
subtitle: "Impact of Covid 19 on Number of Marriages"
author: 
  - Ying Wen Bu
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)

data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))
```


# Introduction

We use @talia, @opendatatorotno, and @rohan.

The remainder of this paper is structured as follows. @sec-mydatasection



# Data {#sec-mydatasection}

Some of our data is of marriage numbers (@fig-marriage), from @opendatatoronto.

```{r}
#| label: fig-marriage
#| fig-cap: Bills of penguins
#| echo: false

data |> 
  ggplot(aes(x = date, y = marriage_licenses)) +
  geom_point()
```
The marriage numbers have been generally stable before the pandemic, although the exact numbers in different locations vary a lot.The number significantly decreased after 2020, then had a very sharp increase after 2022, exceeding the average amount before 2020. This suggests that less people got married during the pandemic, and most of them likely delayed their marriage towards the end of the lockdown, contributing to the large number of marriages at that time.
