---
title: "Toronto Citizens' Opinion on A Future Casinos"
subtitle: "For vs. Against And General Preferences"
author: 
  - Ying Wen Bu
thanks: "Code and data are available at: https://github.com/annie142857/starter_folder/tree/main"
date: 19 September 2024
date-format: long
abstract: "This study takes results from a Toronto City Manager's survey on people's opinion on the construction of a casino. (results). Although the survey was conducted to incorporate people's viewpoint into the casino's construction, the results can still be used in other research to investigate people's opinions on casinos and related entertainments."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)

approval <- read_csv(here::here("C:/Users/86189/Desktop/STA304A1/outputs/data/clean_data(approval).csv"), show_col_types = FALSE)

standalone <- read_csv(here::here("C:/Users/86189/Desktop/STA304A1/outputs/data/clean_data(standalone).csv"), show_col_types = FALSE)

```


# Introduction

We use @citeR, @tidyverse, @dplyr, @opendatatoronto, @ggplot2

The remainder of this paper is structured as follows. 



# Data {#sec-datasection}

```{r}
#| echo: false
#| eval: true
#| warning: false
#| label: fig-approval
#| fig-cap: "Attitude towards A New Casino"
#| fig-subcap: ["How you feel about a new casino?","Does a casino fit your image of the city?"]
#| layout-ncol: 2

approval |>
  ggplot(aes(x = feeling, fill = Gender)) +
  geom_bar() +
  theme_classic() +
  labs(x = "Feeling about having a new casino", y = "Number of respondents")

approval |>
  ggplot(aes(x = image, fill = Gender)) +
  geom_bar() +
  theme_classic() +
  labs(x = "Does it fit the image of the city", y = "Number of respondents")
```

Participants were asked on their feelings about having a new casino in Toronto, as shown in @fig-approval-1, where 1 means strongly opposed and 5 means strongly in favor. Almost 10000 participants strongly opposed the new casino, which is over half of the respondents. This tendency is slightly higher in women. Due to the low number of transgender participants, no observation can be drawn on their tendencies on this problem. Most of the participants have a strong opinion on this problem, and they either strongly opposed or are strongly in favor of a casino.

Participants were then asked on whether a new casino fit their image of Toronto. This question is similar to the previous question, although it only have four options instead of five. The responses were very similar to those of the previous question, except that the "not at all" option exceeded 10000 respondents, presumably because it contained participants from the two "opposed" options from the previous question.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| label: fig-standalone
#| fig-cap: "How suitable is each type of building?"
#| fig-subcap: ["How suitable is a standalone casino?","How suitable is an integrated entertainment complex?"]
#| layout-ncol: 2

standalone |>
  ggplot(aes(x = standalone, fill = Gender)) +
  geom_bar() +
  theme_classic() +
  labs(x = "Suitability", y = "Number of respondents")

standalone |>
  ggplot(aes(x = integrated, fill = Gender)) +
  geom_bar() +
  theme_classic() +
  labs(x = "Suitability", y = "Number of respondents")
```

Participants were asked to rate the suitability of a standalone casino (fig-standalone-1), and the suitability of an integrated entertainment complex casino (fig-standalone-2). In the graphs, 1 means strongly unsuitable, and 5 means strongly suitable. For both types of buildings, the majority of participants selected "strongly unsuitable". This tendency is slightly higher in women and in people who preferred to not disclose their gender. Nothing can be drawn on transgender people because their number is too low. Around 10000 participants found a standalone casino strongly unsuitable, while this number is lower than 9000 for an integrated entertainment complex, showing a slightly higher tolerance of an integrated entertainment complex.

# Results





# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}


# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check




\newpage


# References