---
title: "Toronto Citizens' Opinion on A Future Casinos"
subtitle: "For vs. Against And General Preferences"
author: 
  - Ying Wen Bu
thanks: "Code and data are available at: https://github.com/annie142857/starter_folder/tree/main"
date: 19 September 2024
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)

approval <- read_csv(here::here("C:/Users/86189/Desktop/STA304A1/outputs/data/clean_data(approval).csv"), show_col_types = FALSE)

```


# Introduction

We use @citeR, @tidyverse, @dplyr, @opendatatoronto, @ggplot2

The remainder of this paper is structured as follows. 



# Data {#sec-datasection}

```{r}
#| echo: false
#| eval: true
#| warning: false
#| label: fig-approval
#| fig-cap: "Attitude towards A New Casino"
#| fig-subcap: ["How you feel about a new casino?","Does a casino fit your image of the city?"]
#| layout-ncol: 2
#| 
approval |>
  ggplot(aes(x = feeling, fill = Gender)) +
  geom_bar() +
  theme_classic() +
  labs(x = "Feeling about having a new casino", y = "Number of respondents")

approval |>
  ggplot(aes(x = image, fill = Gender)) +
  geom_bar() +
  theme_classic() +
  labs(x = "Does it fit the image of the city", y = "Number of respondents")
```

Participants were asked on their feelings about having a new casino in Toronto, as shown in @fig-approval-1, where 1 means strongly opposed and 5 means strongly in favour.



# Results





# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}


# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check




\newpage


# References